\section*{ForTheL Preamble}

\begin{forthelfull}
[set/-s] [element/-s] [belong/-s]

Signature Set. A set is a notion.
Signature Element. 
    Let S be a set.
    An element of S is a notion.

Let x << S denote (x is an element of S).
Let x belongs to S denote (x is an element of S).

Definition DefSubset. 
    Let S be a set.
    A subset of S is a set T such that every (x << T) belongs to S.

Let S [= T denote (S is a subset of T).

Definition DefPowerSet. 
    Let S be a set.
    The power set of S is the set P such that
    for every (x << P) x is a subset of S.

Let P = 2^S denote (P is the power set of S).

[pair/-s]

Signature Pair. A pair is a notion.

Signature FirstElementPair.
    Let Q be a pair.
    The first element of Q is a notion.

Signature SecondElementPair.
    Let Q be a pair.
    The second element of Q is a notion.

Let Q = (x,y) denote (Q is a pair and x is the first element of Q and y is the second element of Q).
Let (x,y) denote (for some pair Q x is the first element of Q and y is the second element of Q).

Definition DefCartesianProduct. 
    Let S,T be sets.
    The cartesian product of S and T is the set U such that
    ((x,y) << U) for every (x << S), (y << T).

Let SxT denote (the cartesian product of S and T).

Definition DefRelationOn. 
    Let S be a set.
    A relation on S is a subset R of SxS.

Let xRy denote ((x,y) << R).    

Definition DefReflexiveRelationOn. 
    Let S be a set.
    A reflexive relation on S is a relation R on S such that
    xRx for every (x << S).

Definition DefAntiSymmetricRelationOn. 
    Let S be a set.
    An antisymmetric relation on S is a relation R on S such that
    (xRy and yRx => x = y) for every (x << S, y << S).

Definition DefTransitiveRelationOn.
    Let S be a set.
    A transitive relation on S is a relation R on S such that
    (xRy and yRz => xRz) for every (x << S, y << S, z << S).
\end{forthelfull}
